\documentclass[11pt, a4paper]{moderncv}

\moderncvstyle{banking} % 'banking' style is clean and supports themes
\moderncvcolor{red}     % Sets the red theme

\usepackage[scale=0.8,
            top=1.5cm,
            bottom=1.5cm,
            left=1.25cm,
            right=1.25cm]{geometry} % For spacing
\usepackage{fontawesome5}          % For icons

% Changing the size of my name
\renewcommand*{\namefont}{\fontsize{16}{18}\selectfont}

% Personal information
\name{Amirhossein}{Najafizadeh}
\address{East Setauket, NY}
\phone{+1 (123) 456-7890}
\email{Amirhossein.Najafizadeh}
\social[linkedin]{linkedin.com/in/amirnhnajafiz21}
\social[github]{github.com/amirhnajafiz}

\begin{document}

% Building the title (-1cm is needed to reduce the next space)
\makecvtitle
\vspace{-1cm}

\section{Education}
\cventry{Aug 2024 -- Aug 2029}{Ph.D. in Computer Science}{Stony Brook University}{Stony Brook, New York}{GPA: 3.92}{
    \textbf{Relevant Coursework:} System Security, Distributed Systems, Computer Networks, Visualization\\
    \textbf{Scholarships:} Awarded a one-year full scholarship for being among the top applicants}
\cventry{Aug 2018 -- Dec 2023}{Bachelor of Engineering in Computer Engineering}{Amirkabir University (Tehran Polytechnic)}{Tehran, Iran}{GPA: 3.63}{
    \textbf{Relevant Coursework:} Cloud Computing, Data Security, Database Design, Web Engineering\\
    \textbf{Honors:} Graduated among top 10\% of class 2024}

\section{Technical Skills}
\cvitem{Programming Languages}{Go, Python, ShellScript (5 years), C, JavaScript (4 years), C++, Java (2 years)}
\cvitem{Operating Systems}{Linux, Ubuntu, Debian, MacOS, Windows (5 years)}
\cvitem{Cloud Systems}{Kubernetes, OpenShift (3 years), OpenStack, VMware vSphere (1 year)}
\cvitem{Storage Systems}{SQL/MySQL, PostgreSQL, MongoDB, Redis (4 years), Prometheus (2 years)}

\section{Professional Experience}
\cventry{Nov 2023 -- Aug 2024}{Cloud Engineer}{Snapp Cloud!}{Tehran, Iran}{}{
    \begin{itemize}
        \item Maintained and deployed Operators on Kubernetes and OpenShift platforms, utilizing tools such as OLM and Helm Charts for applications including StreamZ, RedisCluster, and PostgreSQL.
        \item Developed Kubernetes Operators, including the Ceph-S3 Operator and Quota Operator.
        \item Managed centralized monitoring tools such as Prometheus, Grafana, Loki, and Thanos.
        \item Facilitated application delivery using ArgoCD for both public and private applications.
        \item Managed over 1,000 VMs, 200 bare-metal servers, and 5 clusters using OpenShift and OpenStack.
    \end{itemize}}
\cventry{Nov 2021 -- Oct 2023}{Software Engineer}{Snapp}{Tehran, Iran}{}{
    \begin{itemize}
        \item Manage central message queues and real-time services, utilizing technologies such as NATS, EMQX, and Kafka.
        \item Administer the shared cabs’ panel and reporting services using Go, Redis, and MySQL.
        \item Implement user authentication for EMQX clusters using Go.
        \item Develop and support in-app communication tools, including call and chat functionalities using Go and WebRTC.
    \end{itemize}}

\section{Academic Research \& Projects}
\cventry{Jan 2025 -- Present}{Multi-cloud Hybrid GPU Clusters for AI Workloads}{Stony Brook University}{Stony Brook, New York}{}{
    \begin{itemize}
        \item Set up a 3-node Kubernetes cluster using Ansible and Terraform to utilize NVIDIA GPU cards.
        \item Migrated cluster storage to NFS to enable a transition to high-speed GPFS storage.
        \item Investigated AI/ML workload performance on running nodes.
        \item Developed a prediction model to forecast GPU performance for workloads.
        \item Rescheduled AI/ML jobs based on performance using a custom scheduler called Autopilot by IBM.
    \end{itemize}}
\cventry{Feb 2025 -- Apr 2025}{Telescope Proxy: Smart ABR for InterPlanetary File System}{Stony Brook University}{Stony Brook, New York}{}{
    \begin{itemize}
        \item Built a proxy using Go-Fiber to enhance video streaming with IPFS as the storage backend.
        \item Dynamically adjusted bandwidth predictions by incorporating probabilistic models for replica selection, enabling more accurate quality adaptation in multi-replica environments.
        \item Replaces stateful proxy servers with scalable, stateless services.
        \item Added File-based segment cache tracking system for better cache management.
        \item Collected real-time metrics with Prometheus and implemented distributed tracing using OpenTelemetry (Jaeger).
    \end{itemize}}
\cventry{May 2022 -- Dec 2023}{PTaaS (Penetration Testing as a Service)}{Amirkabir University}{Tehran, Iran}{}{
    \begin{itemize}
        \item Developed a full-stack service using Golang, Vue.js, and PostgreSQL to perform automated penetration testing.
        \item Used Nmap to detect system vulnerabilities.
        \item Wrote simple Go scripts to perform various tests.
        \item Developed an orchestration system to run tests in parallel within isolated environments.
    \end{itemize}}

\section{Independent Projects}
\cvitem{NFS Metrics Exporter}{Technologies: Go, Prometheus, NFS
    \begin{itemize}
        \item Developed a cloud native Prometheus exporter for exporting NFS computation metrics from client side.
    \end{itemize}}
\cvitem{Amazon EC2 Practice}{Technologies: Go, PostreSQL, Docker, NginX, Kubernetes, Ansible, Terraform
    \begin{itemize}
        \item Built a full-stack application (frontend, backend, and database), containerized it with Docker, and deployed it with Nginx on a system provisioned with Ansible and Terraform. Provided Docker images and Helm charts for Kubernetes deployment.
    \end{itemize}}
\cvitem{MQTT Blackbox Exporter}{Technologies: Go, Prometheus, Jaeger, EMQX, Helm Charts
    \begin{itemize}
        \item Developed a system to connect, subscribe and publish over MQTT broker to check its status.
    \end{itemize}}
\cvitem{Apaxos}{Technologies: Go, MongoDB, PAXOS, gRPC
    \begin{itemize}
        \item Developed a distributed transaction management service designed to replicate transactions across multiple nodes, ensure data consistency, and tolerate node failures. To achieve these goals, a modified version of the PAXOS consensus protocol was used to support multiple values in a single instance.
    \end{itemize}}
\cvitem{PBFT}{Technologies: Go, MongoDB, PBFT, TLS/SSL, Threshold Signature
    \begin{itemize}
        \item Developed a transaction management system that operates in an insecure environment using the Linear-PBFT consensus protocol, implementing both normal operation and view-change routines.
    \end{itemize}}
\cvitem{System-call Blocker}{Technologies: C, eBPF, BCC, LSM
    \begin{itemize}
        \item Used eBPF and LSM probes to block file creation, command execution, and network connections for subjects.
    \end{itemize}}
\cvitem{ELK Operator}{Technologies: Go, Operator-SDK, Kubernetes
    \begin{itemize}
        \item A Kubernetes operator for setting up Elasticsearch, Logstash, and Kibana instances on your cluster.
    \end{itemize}}
\cvitem{SafeX}{Technologies: C, Ptrace, Function-hooking
    \begin{itemize}
        \item Built a sandboxing tool that redirects file writes to \texttt{/tmp} and blocks access to paths listed in \texttt{\textasciitilde{}/.safenoread}.
    \end{itemize}}

\section{Leadership Experience}
\cventry{Aug 2024 -- Dec 2024}{Operating Systems Teaching Assistant}{Stony Brook University}{Stony Brook, New York}{}{
    \begin{itemize}
        \item Led lab and recitation sessions for 40 students, focusing on operating systems, Linux, and XV6.
        \item Collaborated with faculty and fellow TAs to design and evaluate assignments, provide one-on-one student support, and enhance course materials.
    \end{itemize}}
\cventry{Jan 2023 -- May 2023}{Cloud Computing Teaching Assistant}{Amirkabir University}{Tehran, Iran}{}{
    \begin{itemize}
        \item Led lab sessions for 70 students, teaching virtualization, QEMU, Docker, and Kubernetes.
        \item Delivered live sessions on practical Docker and Kubernetes usage for developers.
    \end{itemize}}
\cventry{Apr 2022 -- May 2022}{Secretary and organizer of the 13th Linux Festival}{Amirkabir University}{Tehran, Iran}{}{
    \begin{itemize}
        \item Organized a weekly festival focused on Linux and open-source projects.
        \item Hosted over 14 technical talks and workshops for more than 120 participants.
    \end{itemize}}

\section{Publications \& Recognitions}
\cvitem{Publication}{Amir Zadeh. \textit{Having Your Kubernetes Over NFS}. Published on the ITNEXT platform on Medium. Visit at \url{https://itnext.io/having-your-kubernetes-over-nfs-0510d5ed9b0b}}
\cvitem{Publication}{Amir Zadeh, Seyed Ahmad Javadi. \textit{Jump Over Golang Channels: A Method to Prioritize Tasks in Go Channel Queues}. This paper presents a solution to bypass low-priority tasks in Golang channel queues and compares its performance to traditional Go channels. Published on ResearchGate. Visit at \url{http://dx.doi.org/10.13140/RG.2.2.28045.92646}}

\end{document}
